Assignment 5

### 2015-03-03 rmtw/a5/latex8.tex
yolo

Once papers were selected, the following data was selected: Publication year, topic area, methodology type, authors, summary of the paper, conclusion. This data was the used as a base for analysis when evaluating the research questions for each paper.

@@

\SubSection{Conducting the Study}
\textbf{Conducting the review}
\begin{itemize}
\item Identification of research (6.1)

@@

\item Selection of primary studies (6.2)

@@

\item Study Quality Assessment (6.3) x

@@

\item Data extraction and monitoring (6.4) x

@@

\item Data synthesis x
\end{itemize}

\SubSection{Reporting (probably skip)}
\textbf{Reporting the review}
\begin{itemize}
\item Specifying dissemination mechanisms (7.1)

As the the results will be intended to have some impact upon whether or not MDSD is adopted in practice. As such the results will ideally be disseminated via journals, publications and via web pages to reach a broad audience.

\item Formatting the main report (7.2)
\item Evaluating the report (7.3)
\end{itemize}

@@

\begin{itemize}
\item \textbf{these bulletins are from the assignment specification}
\item Describe and explain the research strategy (i.e. SLR) and investigation methods that will be used for the study. 
\item Motivate your choice of experiment using relevant references. 
\item Search string including keywords and used databases
\item inclusion/exclusion criteria
\item data extraction
\item data synthesis
\item quality assessment
\end{itemize}

>>>>

@@

\SubSection{Conducting the Study}

@@

@@

@@

@@

Data synthesis x

@@
